% !TEX encoding = UTF-8 Unicode
%!TEX root = thesis.tex
% !TEX spellcheck = en-US
%%=========================================
\chapter{Introduction}
Introduction to the problem, some background about the Survey Explorer project..

%%=========================================
\section{Background}
Where do we stand? What has been done before?
%%=========================================
\subsection*{Problem Formulation}

%%=========================================
\subsection*{Literature Survey}

%%=========================================
\subsection*{What Remains to be Done?}
...
%%=========================================
\section{Objectives}
The main objectives of this project are
\begin{enumerate}
\item Investigate existing solutions for HIL testing of autonomous boat
\item Describe implementation of sensors and data processing on Odin and/or Jolner for situational awareness above the surface.
\item Discuss complexity and solutions related to simulation of raw sensor data from Radar, Lidar and camera versus simulation of pre-processed data.  
\item Specify interface between simulator and autonomous navigation system.
\item Specify system for logging and visualization of simulation in real-time and for post simulation analysis.
\item Necessary protyping in C++ and MATLAB to verify assumptions.
\item Investigate which other agents (ships, small boats etc.) that can be interesting to implement as a part of the simulation environment.
\item Discuss methods for using the model as a part of an automized test environment related to ROS, MROS, scripting, repetition and regression testing.
\end{enumerate}

%%=========================================
\section{Limitations}

%%=========================================
\section{Approach}

%%=========================================
\section{Structure of the Report}
The rest of the report is organized as follows. Chapter 2 gives an introduction to \ldots
